---
title: "Reproducing Dual Practice Table 5 results"
author: "Carlos Paramo"
date: "3/29/2021"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls())

library(tidyverse)
library(magrittr)
library(sandwich)
library(ggplot2)
#library(causalTree)
library(rpart)
library(grf)
library(rpart.plot)
library("foreign")
library("xtable")
library(glmnet)
library(gridExtra)
library(multiwayvcov)
library(miceadds)

# options
options("scipen"=100, "digits"=4)

# define a function for easy string pasting
"%&%" <- function(x, y) paste(x, y, sep="")

setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # sets working directory to source file location

# Import Data with PMT covariates
SPdata <- haven::read_dta("../Data/SPDataset.dta")
```


# Introduction:

This file replicates the results from table 5 using the dual practice sample. Our outcome of interest is the probability of giving the correct treatment. 

## No controls and SP fixed effects

```{r}
# Comditional data:
tmp <- SPdata[SPdata$dual ==1 & SPdata$round == 2 & SPdata$case!=2, ]
# Linear regression: 
model1 <- lm.cluster(correct_treat ~ private + case3 + ssp2 + ssp3 +ssp4 +ssp5 +ssp6 +ssp7 +ssp8 +ssp9 +ssp10 +ssp11 +ssp12 +
     ssp13 +ssp14 +ssp15, data = tmp, cluster = tmp$finprovid)

summary(model1)
```

## No controls and SP + district fixed effects

```{r}
# Comditional data:
tmp <- SPdata[SPdata$dual ==1 & SPdata$round == 2 & SPdata$case!=2, ]
tmp$distid <- as.factor(tmp$distid)
# Linear regression: 
model2 <- lm.cluster(correct_treat ~ private + case3 + ssp2 + ssp3 +ssp4 +ssp5 +ssp6 +ssp7 +ssp8 +ssp9 +ssp10 +ssp11 +ssp12 +
     ssp13 +ssp14 +ssp15 + distid, data = tmp, cluster = tmp$finprovid)

summary(model2)
```

## Controls, and district + SP fixed effects:

```{r}
# Comditional data:
tmp <- SPdata[SPdata$dual ==1 & SPdata$round == 2 & SPdata$case!=2, ]
tmp$distid <- as.factor(tmp$distid)
# Linear regression: 
model3 <- lm.cluster(correct_treat ~ private + case3 + age + gender + numafter + ssp2 + ssp3 +ssp4 +ssp5 +ssp6 +ssp7 +ssp8 +ssp9 +ssp10 +ssp11 +ssp12 +
     ssp13 +ssp14 +ssp15 + distid, data = tmp, cluster = tmp$finprovid)

summary(model3)
```


# Robustness Check: 


## See whether the prefered specification (panel b) has similar behavior when using probit model:

```{r}
# Comditional data:
tmp <- SPdata[SPdata$dual ==1 & SPdata$round == 2 & SPdata$case!=2, ]
tmp$distid <- as.factor(tmp$distid)
# Linear regression: 
model4 <- glm.cluster(data = tmp,correct_treat ~ private + case3 + ssp2 + ssp3 +ssp4 +ssp5 +ssp6 +ssp7 +ssp8 +ssp9 +ssp10 +ssp11 +ssp12 +
     ssp13 +ssp14 +ssp15 + distid, cluster = tmp$finprovid, family = binomial(link = "probit"))

summary(model4)
```

To interpret this, note that the probability of a public clinic providing a correct treatment is 0.373 (table 5), which is a z score of -0.31, since private increases the z score by 0.54 accorrding to the probit model, then the probability of private is 0.59, so there is a 0.21 increase in probability. This is larger than the originally reported results, but within any reasonable margin of error. This is a rough estimate, but shows that this model leads to similar results relative to the linear model. 


## Panel c Probit version: 

```{r}
# Comditional data:
tmp <- SPdata[SPdata$dual ==1 & SPdata$round == 2 & SPdata$case!=2, ]
tmp$distid <- as.factor(tmp$distid)
# Linear regression: 
model4 <- glm.cluster(data = tmp,correct_treat ~ private + case3 + age + gender + numafter + ssp2 + ssp3 +ssp4 +ssp5 +ssp6 +ssp7 +ssp8 +ssp9 +ssp10 +ssp11 +ssp12 +
     ssp13 +ssp14 +ssp15 + distid, cluster = tmp$finprovid, family = binomial(link = "probit"))

summary(model4)
```

Here we find a similar pattern as before, where including controls increases the overall effect of being a private practice. 

## No controls and SP + district fixed effects, using all cases (not dropping dyseny):

```{r}
# Comditional data:
tmp <- SPdata[SPdata$dual ==1 & SPdata$round == 2, ]
tmp$distid <- as.factor(tmp$distid)
# Linear regression: 
model2 <- lm.cluster(correct_treat ~ private + case3 + case2 + ssp2 + ssp3 +ssp4 +ssp5 +ssp6 +ssp7 +ssp8 +ssp9 +ssp10 +ssp11 +ssp12 +
     ssp13 +ssp14 +ssp15 + distid, data = tmp, cluster = tmp$finprovid)

summary(model2)
```

## Alternative Controls (age squared), and district + SP fixed effects:

```{r}
# Comditional data:
tmp <- SPdata[SPdata$dual ==1 & SPdata$round == 2 & SPdata$case!=2, ]
tmp$distid <- as.factor(tmp$distid)
tmp$age2 <- tmp$age^2
# Linear regression: 
model3 <- lm.cluster(correct_treat ~ private + case3 + age + age2 + gender + numafter + ssp2 + ssp3 +ssp4 +ssp5 +ssp6 +ssp7 +ssp8 +ssp9 +ssp10 +ssp11 +ssp12 +
     ssp13 +ssp14 +ssp15 + distid, data = tmp, cluster = tmp$finprovid)

summary(model3)
```


